Output Summary

### 2020-10-21 03-post-process/output-plots.Rmd
Add some numerical summaries to output plots

---
title: "Output Summary"
subtitle: "`r c('CAT' = 'Catherine Creek', 'LOS' = 'Lostine', 'UGR' = 'Upper Grande Ronde')[params$pop]`"
output: html_document
params:
  pop:
    label: "Population"
    value: CAT
    input: select
    choices: [CAT, LOS, UGR]
  mcmc_plots:
    label: "Make MCMC Plots"
    input: checkbox
    value: FALSE
editor_options: 
  chunk_output_type: console
---

@@

>>>>

---
title: "Output Summary"
subtitle: "`r c('CAT' = 'Catherine Creek', 'LOS' = 'Lostine', 'UGR' = 'Upper Grande Ronde')[params$pop]`"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  pop:
    label: "Population"
    value: CAT
    input: select
    choices: [CAT, LOS, UGR]
  mcmc_plots:
    label: "Make MCMC Plots"
    input: checkbox
    value: FALSE
editor_options: 
  chunk_output_type: console
---

@@

# Numerical Summaries

## Recruitment Function

```{r}
# extract posterior summaries
alpha_summ = post_summ(post, "alpha", digits = 0)
beta_summ = post_summ(post, "beta", digits = -3)
sigma_summ = post_summ(post, "sigma_Pb", digits = 2)

# create/format the table
tab = cbind(alpha_summ, beta_summ, sigma_summ)
colnames(tab) = c("$\\alpha$", "$\\beta$", "$\\sigma_{Pb}$")

# produce html table
kable(tab, format.args = list(big.mark = ","), escape = F) %>%
  kable_styling(full_width = F, bootstrap_options = "condensed") %>%
  column_spec(1, bold = T)
```

## Carcass Correction Factors

```{r}
# extract posterior summaries
carc_adj = post_summ(post, "carc_adj", digits = 1)

# create/format table
x = paste0(carc_adj["mean",], " (", carc_adj["2.5%",], " -- ", carc_adj["97.5%",], ")")
names(x) = colnames(carc_adj)
tab = array_format(x)
colnames(tab) = c("Female", "Male")
rownames(tab) = c("Age 3", "Age 4", "Age 5")

# produce html table
kable(tab) %>%
  kable_styling(full_width = F, bootstrap_options = "condensed") %>%
  column_spec(1, bold = T)
```
